Estimating Information Transfer from Different Data Sources via Precise Bias-variance Asymptotics

### 2021-07-10 revision_journal/multitask.tex
finish sec 4 edits

%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
%We provide a sharp generalization error bound of hard parameter sharing estimators.

%Hard parameter sharing is a commonly used architecture in multi-task learning. However, there have been few theoretical results on the performance of the HPS estimators in high-dimensional multi-task learning. In this section, we extend our results on the predication loss of the HPS estimator to a multi-task linear regression, where all tasks have the same covariates. We make this extension for the following reasons. First, its restriction to the two-task case provides a rare example where the output layers $A_1$ and $A_2$ can be characterized exactly. Second, the proof of the multi-task case is no harder than the two-task case, but it can provide much clearer geometric intuition  as we will discuss below. Third, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}. Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
%It is not hard to extend the above result to the cases with more than two tasks. {\cor For the general case, we study them in a future work.}

%Suppose we have $t$ datasets.
%For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
%Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
%We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
%We study the standard hard parameter sharing architecture:
%a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
%See Figure \ref{fig_intro_arch} for an illustration.
%The width of $B$, denoted by $r$, plays an important role in regularization.
%As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
%Hence, we assume that $r < t$ in our study.
%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
%We study the following minimization problem:
%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
%	The size of each set is described below.
%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
%\vspace{-0.1in}
%\begin{align}\label{eq_mtl}
%			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
%\end{align}
%\vspace{-0.05in}
%where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.

@@

\paragraph{Data model.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$. The label vector of the $i$-th task follows a linear model
\begin{align}
    Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}, \text{ for } i=1, 2,\cdots, t.
\end{align}
We assume several standard conditions on $X$ and each of $\varepsilon^{(i)}$.
First, $X = Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}.
%that is, $Z$ is an $n\times p$ random matrix with i.i.d. entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
Second, every $\varepsilon^{(i)} \in \real^{n}$ is a random vector with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in equation \eqref{eq_highmoments}.
Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from the other linear models, the feature covariates, and all noise vectors.

%\begin{figure*}[!t]
%	\centering
%	\includegraphics[width=0.3\textwidth,valign=t]{figures/mtl_model_arch.pdf}
%	\caption{A hard parameter sharing architecture}
%	\label{fig_intro_arch}
%\end{figure*}
%\begin{enumerate}
%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
%\end{enumerate}

\paragraph{Estimator.} We extend the two-layer linear neural network from equation \eqref{eq_hps} to combine multiple data sources as follows:
\begin{align}
	f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
\end{align}
where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$. %Recall that $r$ is the width of $B$.
We will focus on cases with $r < t$.
Otherwise, the global minimum of $f(A, B)$ reduces to single-task learning, similar to Proposition \ref{prop_large_r} (details omitted).

Let $\hat A$ be the global minimizer of $g(A)$. Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$. We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in
and its (out-of-sample) prediction loss as
\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee

	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
	\begin{align}
		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
	\end{align}
	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
	\begin{align}\label{eq_mtl_output_layer}
		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
	\end{align}
%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$.

\paragraph{Result.} Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace. To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which can be regarded as the covariance of the task labels):
\begin{align}\label{eq_A_star}
	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
\end{align}
where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices.
 To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue. Otherwise, $A^{\star}$ is not well-defined and Theorem \ref{thm_many_tasks} will give a null result.
 %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction. Then we have the following result.

% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
%Our result is stated as follows.

\begin{theorem}\label{thm_many_tasks}
%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant. Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}. Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
	%Let $n = c \cdot p$.
	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
	%that satisfy Assumption \ref{assm_secA2} in the appendix.
	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}.
Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary (small) constant. Then for any task $i = 1,  \cdots, t$, we have that with high probability,
\be\label{minimizer_beta}
\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
\ee
where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$. Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that  with high probability,
	\begin{align}
		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right). \label{Li_multi1}
		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align}
	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$. %and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
Finally, we have a better bound for the averaged prediction loss:  with high probability,
\begin{align}
&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
 &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 .\label{Li_multi2}
\end{align}
\end{theorem}

Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$. Moreover, the factor $(\lambda_r - \lambda_{r+1})^{-1}$ is natural, because the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not stable when $\lambda_r $ and $\lambda_{r+1} $ are close to each other.  The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace. The estimate \eqref{Li_multi1}
 gives the exact asymptotic limit of $L_i(\hat{\beta}_i^{\MTL}(\hat a))$, which shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$. Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases for the multi-task HPS estimator. On the other hand, the bias term always increases (because the bias in single-task linear regression is zero). Hence as in the transfer learning setting, whether the HPS estimator is better than the OLS estimator depends on an intricate  {bias-variance tradeoff}.
%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
%On the other hand, the bias always increases.}
We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$. Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique. For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.

The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.

@@

\begin{example}%[Random-effect model]
\label{ex_same_cov}
%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
%More precisely, %we have
Suppose that {$\beta^{(i)}=\beta_0 +\wt \beta^{(i)}$} for $ i=1,2,\cdots, t,$
where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
and $\wt \beta^{(i)}$ denotes the $i$-th
%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
%Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
%The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.

@@

@@

Comparing the above equation with \eqref{L_STL_simple01} (and ignoring the small error), we have the following observations.

@@

%\begin{enumerate}
\begin{enumerate}
	\item {\bf Positive vs. negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.

	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$. Hence increasing the width $r$ of the shared feature representation layer does not help.
	%To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).

%	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$. Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression. More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
%	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability. }\]
%	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
%	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$
%	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.
	%samples that is less than $n$ samples to get comparable loss to STL.
	%This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
	\end{enumerate}
\end{example}

>>>>

@@

\paragraph{Data model.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$. The label vector of the $i$-th task follows a linear model
\begin{align}\label{eq_mtl_data}
    Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}, \text{ for } i=1, 2,\cdots, t.
\end{align}
Similar to Section \ref{sec_main}, we use the first $(t-1)$ datasets as sources to predict the $t$-th task.
However, there is a \text{model shift} between the data sources and the task we would like to predict.
We make several standard assumptions on $X$ and each of $\varepsilon^{(i)}$.
First, $X = Z\Sigma^{1/2}$ is a random matrix satisfying Assumption \ref{assm_big1} (same as $X^{(2)}$).
In particular, the sample size $n$ is greater than the dimension $p$.
Second, every $\varepsilon^{(i)} \in \real^{n}$ is a random vector with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments up to any order (cf. equation \eqref{eq_highmoments}).
Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from any other $\beta^{(j)}$ for $j \neq i$, the matrix $X$, and $\varepsilon^{(j)}$ for any $j$.

\paragraph{Estimator.} We combine multiple data sources by extending the two-layer linear neural network from equation \eqref{eq_hps} as follows:
\begin{align}
	f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
\end{align}
where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ denotes the output layer and $B \in \real^{p \times r}$ denotes the (shared) feature layer.
We set the width of the feature layer $r$ less than the number of tasks $t$.
Otherwise, when $r \ge t$, the global minimum of $f(A, B)$ reduces to single-task learning, similar to Proposition \ref{prop_large_r} (details omitted).

Let $(\hat A, \hat B)$ denote a global minimizer of $f(A, B)$.
We define the HPS estimator for task $t$ as $\hat \beta_t^{\MTL} := \hat B \hat A_i$, where $\hat A_i$ denotes the $i$-th column of $\hat A$.
We evaluate the performance of $\hat{\beta}_t^{\MTL}$ according to its excess risk:
\be\label{ith_loss}
    L_t(\hat{\beta}_t^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta}^{\MTL}_t - \beta^{(t)}\right)}^2.
\ee

\paragraph{Result.} We show that in the multi-task setting, hard parameter sharing finds the ``best'' rank-$r$ approximation to all tasks.
To formally describe our result, we introduce several notations.
Let $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ be the concatenated model vectors of all tasks.
Let $A^{\star} {A^{\star}}^{\top}$ be the best rank-$r$ approximation of ${B^{\star}}^\top\Sigma B^{\star}$ in the following sense:
\begin{align}\label{eq_A_star}
	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
\end{align}
where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices.
Let $a_i^{\star}\in\real^r$ be the $i$-th column vector of $A^{\star}{A^{\star}}^{\top}$.
We characterize the excess risk $L_t(\hat{\beta}_t^{\MTL})$ precisely in the following result.

\begin{theorem}[Excess risk of HPS for multiple tasks under model shift]\label{thm_many_tasks}
Suppose the multi-task setting according to equation \eqref{eq_mtl_data} holds.
Let $r$ be any positive integer less than $t$.
Suppose the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than its $(r+1)$-th largest eigenvalue. 
Let $c>0$ be an arbitrary (small) constant.
The following estimates for $L_t(\hat{\beta}_t^{\MTL})$ holds with high probability:
\begin{align}
	\bigabs{L_t(\hat{\beta}_t^{\MTL}) - L_t(B^{\star}a_t^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_t^{\star}}^2  } 
	\le  \sqrt{\bignorm{{B^\star}^\top\Sigma B^\star}_{\op} \cdot n^{-\frac 1 2+ \frac 2{\varphi} + c}  + \sigma^2 n^{-\frac 1 2 + c}} \cdot \frac{\bignorm{{B^\star}^\top\Sigma B^\star}_{\op}+  \sigma^2}{\lambda_r - \lambda_{r+1}}. \label{Li_multi1}
\end{align}
	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$. %and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
%Finally, we have a better bound for the averaged prediction loss:  with high probability,
%\begin{align}
%&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
% &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 .\label{Li_multi2}
%\end{align}
\end{theorem}

Recall that $\varphi > 4$ according to Assumption \ref{assm_big1}, thus, $\frac {2}{\varphi} \le \frac 1 2$ and $n^{-\frac 1 2 + \frac 2 {\varphi} + c}$ vanishes to zero for a small enough constant $c$.
Therefore, equation \eqref{Li_multi1} precisely characterizes the excess risk of the HPS estimator.
As a remark, the same result applies to any other tasks although we have focused on predicting task $t$.
Theorem \ref{thm_many_tasks} significantly extends the two-task model shift setting of Theorem \ref{cor_MTL_loss}.
The term $L_t(B^{\star} a_t^{\star})$ captures the bias of the HPS estimator and $\frac{p \sigma^2}{n - p} \bignorm{a_t^{\star}}^2$ captures the estimator's variance.
%The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace. The estimate \eqref{Li_multi1}
% gives the exact asymptotic limit of $L_i(\hat{\beta}_i^{\MTL}(\hat a))$, which shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$. Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases for the multi-task HPS estimator. On the other hand, the bias term always increases (because the bias in single-task linear regression is zero). Hence as in the transfer learning setting, whether the HPS estimator is better than the OLS estimator depends on an intricate  {bias-variance tradeoff}.
%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
%On the other hand, the bias always increases.}
%We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$. Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique. For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.
%	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
%	\begin{align}
%		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
%		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
%	\end{align}
%	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
%	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
%	\begin{align}\label{eq_mtl_output_layer}
%		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
%	\end{align}
The proof of Theorem \ref{thm_many_tasks}, which is based on a characterization of the global minimum of problem \eqref{eq_mtl_same_cov}, can be found in Section  \ref{app_proof_error_same_cov}.

@@

\begin{example}[How to set the width $r$ in HPS?]
\label{ex_same_cov}
%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
%More precisely, %we have
An important question in applications of HPS is how to set the width $r$ of the feature layer.
We use our estimates to show that the optimal width depends on the tradeoff between the estimator's bias and variance.
Concretely, consider a random-effect model where all tasks share a model vector $\beta_0$ plus perturbations.
For every $i=1,2,\cdots, t,$, $\beta^{(i)}=\beta_0 +\wt \beta^{(i)}$}, where $\wt \beta^{(i)}$ denotes the $i$-th
%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $\frac {\kappa^2} p$.

\begin{claim}
\begin{enumerate}
	\item {\bf Positive vs. negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.

	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$. Hence increasing the width $r$ of the shared feature representation layer does not help.
\end{enumerate}
\end{claim}

@@

\begin{proof}

@@

@@

\end{proof}
\end{example}
